Hydras, Ordinals \& Co. \\ A library in Coq of entertaining formal mathematics

### 2021-10-13 doc/JFLA2022/paper.tex
more on Gaia

In order to prove formally that the length of the
kind of hydra battles we consider is not given by a primitive recursive function, we chose to use a formalization of the primitive recursive functions that was originally part of Russell O'Connor's statement and proof of G\"{o}del's first incompleteness theorem~\cite{OConnor05, Goedel}.
For this purpose, and above all in consideration of the scientific interest of this contribution, we decided to host and maintain O'Connor's work in \community.

@@

>>>>

In order to prove formally that the length of the
kind of hydra battles we consider is not given by a primitive recursive function, we chose to use a formalization of the primitive recursive functions that was originally part of Russell O'Connor's formalization of G\"{o}del's first incompleteness theorem~\cite{OConnor05, Goedel}.
For this purpose, and above all in consideration of the scientific interest of this contribution, we decided to host and maintain O'Connor's work in \community.

@@

The data types for ordinals in Cantor and Veblen form are essentially defined the same way in Gaia and \Hydras, but they are not identical inside Coq, e.g., due to placement in different modules. Moreover, there are small differences in the implementation of ordinal arithmetic due to different evolutionary paths taken from the ancestral Cantor library.

Nevertheless, we were able to establish a correspondence between both implementations of ordinals through rewriting lemmas. For instance, we proved that multiplication of ordinals in Cantor normal form in \Hydras refine Gaia's corresponding multiplicate, and could import Gaia's proof of associativity of this multiplication almost for free.
